### 2018-06-18 pubs/itp-2018/sections/proof-reconstruction/strip.tex
Introduction of the strip part reviewed

Unluckily, \Metis does not make explicit in the \TSTP derivation
the way it uses the subgoals to prove the goal. We show that way
in the correctness of the \strip inference rule in Theorem~\ref{thm:strip}.
To show that, we first need to prove Lemma~\ref{lem:inv-uh-lem} and
Lemma~\ref{lem:lem-inv-strip}.

@@

To keep simpler the coming definitions, we use instead of $\fuh_{1}$ function
a unary function defined in~\eqref{eq:uh}.

\begin{align*}
  \label{eq:uh}
  \begin{split}
  &\fuh : \Prop → \Prop\\
  &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
  \end{split}
\end{align*}
Using the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.

@@

>>>>

\begin{remark}
\Metis does not make explicit in the \TSTP derivation the way it uses the
subgoals to prove the goal. We show this approach in the correctness of the
\strip inference rule in Theorem~\ref{thm:strip}. To show this theorem, we prove
Lemma~\ref{lem:inv-uh-lem} and  Lemma~\ref{lem:lem-inv-strip}. In the former, we
introduce the auxiliary function $\fuh_1$ to define the $\fuh$ function used to
define the $\fstrip_1$ function in the latter.
\end{remark}

@@

The second argument in the $\fuh_1$ function is a natural number that constrains
the number of recursive calls. To provide such a number given a formula
$\varphi$, we call the $\fuh_{cm}$ function defined in~\eqref{eq:uh-complexity}.
This function finds what we call the \emph{function complexity} of the function
$\fuh_1$. For the convenience in the following descriptions, we use the
function $\fuh : \Prop → \Prop$ for $\varphi \mapsto \fuh_{1}~φ~(\fuh_{cm}~φ)$.

@@

% \begin{align}
%   \label{eq:uh}
%   \begin{split}
%   &\fuh : \Prop → \Prop\\
%   &\fuh~φ~ = \fuh_{1}~φ~(\fuh_{cm}~φ).
%   \end{split}
% \end{align}

% == CONTINUAR DESDE AQUI
